A Theory of Bidirectional Type Synthesis for Simple Types

### 2023-07-08 tex/sec4-pre-synthesis.tex
[ tex ] Simplify the statement of mode preprocessing

\begin{corollary}[Mode Preprocessing]\label{thm:mode-preprocessing}
  It is decidable for any raw term $V |-_{\Sigma,\erase\Omega} t$ and mode~$\dir{d}$ whether $V |-_{\Sigma,\Omega} \isTerm{t}^\dir{d}$.
\end{corollary}

>>>>

\begin{corollary}[Mode Preprocessing]\label{thm:mode-preprocessing}
  It is decidable whether $V |-_{\Sigma,\Omega} \isTerm{t}^\dir{d}$.%for any raw term $V |-_{\Sigma,\erase\Omega} t$ and mode~$\dir{d}$
\end{corollary}
